---
title: "Prediction model of liver fat in PCOS - validation cohort"
author: "Laura Pyle"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

source('C:/Users/pylell/Documents/GitHub/Functions/01_functions.R')

library(tidyr)
library(magrittr)
library(dplyr)
library(data.table)
library(knitr)
library(pander)
library(pROC)
library(OptimalCutpoints)
library(caret)
library(rms)

set.seed(3654)

# read  data
valid <- read.csv("H:\\Endocrinology\\Green\\Carreau liver fat prediction\\Data\\Validation cohort\\validation cohort.csv")
N <- nrow(valid)

#install.packages("ElemStatLearn", dependencies=T)
library(ElemStatLearn)
library(rpart)
library(rms)

# create HS variable
valid$HS <- ifelse(valid$Liver.Fat>5.5,1,0)

valid_mod <- glm(HS ~ BMI.percentile + Waist.circumference + ALT + SHBG, data=valid,family=binomial(link="logit"))
tabx <- mod_tablog(valid_mod)

# get predicted probability of HS
valid$pred <- predict(valid_mod,type="response",data.frame=valid)
# using the cutoff from our previous model, if probability>0.4399669, assign as predicted to have HS
valid$pred_HS <- ifelse(valid$pred>0.4399669,1,0)

# confusion matrix
conf <- confusionMatrix(as.factor(valid$pred_HS),as.factor(valid$HS),positive='1')
x <- as.matrix(conf)
row.names(x) <- c("Predicted no HS","Predicted HS")
colnames(x) <- c("Observed no HS","Observed HS")
y <- as.matrix(conf,what="overall")
z <- as.matrix(conf,what="classes")
yz <- rbind(y,z)

```

# Background

The purpose of this analysis is to fit the predictive model of hepatic steatosis (HS) that was developed in a test set of adolescent girls with PCOS.  The predictors included in the model were BMI %ile, waist circumference, ALT, and SHBG.

# Methods

The logistic regression model was fit to the validation cohort.  The performance of the model was evaluated using a confusion matrix, and by calculating sensitivity, specificity, and other criteria.

# Results

There were `r N` subjects included in this analysis.  The results of the logistic model are shown below.

```{r, results='asis',tidy=TRUE, echo=FALSE}
kable(x)
```
\

```{r, results='asis',tidy=TRUE, echo=FALSE}
kable(yz)
```

